PubCrawl: A Publication Search Engine

### 2012-05-17 report/paper.tex
Initial writeup of Lucene stuff
Omit actual equations for brevity, since we basically used the scoring as a
black box.

\subsection{Lucene Text Indexing}
%Abhishek

>>>>

\subsection{Document scores}

We use Apache Lucene \cite{lucene} to index documents and provide scores based
on the content of documents. We build the usual inverted index over the corpus,
filtering out stopwords. The structure of the documents is preserved in the XML
corpus, so we can index titles, subtitles, abstracts, and full text as separate
fields. We also include various metadata to simplify the implementation of the
front-end.

Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
Vector Space Model \cite{salton75} to score documents. Documents $d$ and
queries $q$ are vectors $V(\cdot)$ with each term a dimension and coordinates
equal to tf*idf values. Then, the relevance of a document to a query is related
to the angle between them (the cosine similarity score). Lucene generalizes the
cosine similarity score in several ways. First, documents are allowed to have
multiple and duplicate fields. Second, Lucene allows index-time boosting of
documents and fields as well as query-time boosting of query terms. Finally,
Lucene does not require every term to appear in hits, instead using a
coordination factor to score documents which contain more terms higher. These
features can be exploited to improve the quality of search results.
